---
title: "Practical Machine Learning Assignment"
author: "BlueBanana"
date: "Wednesday, August 20, 2014"
output: html_document
keep_md: true
---
The first step is to embed the relevant libraries for machine learning. I also include a library to support multiple processors to speed up the calculation.

```{r}
library(AppliedPredictiveModeling)
library(kernlab)
library(caret)
```

Second step is to read in the training and test data:
```{r}
temp <- tempfile()
download.file("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv",temp)
training <- data.frame(read.table(temp, header = TRUE, sep = ","))
download.file("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv",temp)
test <- data.frame(read.table(temp, header = TRUE, sep = ","))
```

Here I subdivide the data into the training and test set.

```{r}
intrain<-createDataPartition(y=training$classe,p=0.75,list=FALSE)
train2<-training[intrain,]
test2<-training[-intrain,c(2,8,9,10,11,37:49,62:68,84:86)]
testclasse<-training[-intrain,]
```
For the model I choose those variables that showed after an inspection at least some variance and are menaingful for the prediction.

```{r}
train3<- train2[,c(2,8,9,10,11,37:49,62:68,84:86)]
```
For the model estimation I choose the Random Forest method and estimate a model. I do a validation of the model fitness with the test data set.
Finally the model is applied to the target set with the 20 entries. 
```{r}
set.seed(3333)

modelfit <-train(x=train3,y=train2$classe,method="rf")

predictions<-predict(modelfit,newdata=test2)
a<-confusionMatrix(predictions,testclasse$classe)

testvalues<-test[,c(2,8,9,10,11,37:49,62:68,84:86)]

answers<-predict(modelfit,newdata=testvalues)
```

This is the last step, the Model output for the machine grading:
```{r}
  pml_write_files = function(x){
    n = length(x)
    for(i in 1:n){
      filename = paste0("problem_id_",i,".txt")
      write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
    }
  }
  
  pml_write_files(answers)

```